---
title: "COPD 2018-2020 Exacerbation Comparison"
author: "Tessa LiVoti"
date: "Oct. 19, 2020"
output:
  rmdformats::readthedown:
    number_sections: true
    highlight: kate
    mathjax: false
    use_bookdown: true
    cards: true
    css: custom.css
    toc_float: true
      
---

<style type="text/css">
.main-container {
  max-width: 1000px !important;
  margin-left: auto;
  margin-right: auto;
}
div.rect {
  border: 2px solid #cb6328;
  border-radius: 15px;
  padding: 10px;
}
</style>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F, comment="", fig.height=5, fig.pos='H')
library(highcharter)
library(htmlwidgets)
library(kableExtra)
library(htmltools)
library(lubridate)
library(ggplot2)
library(dplyr)
library(Hmisc)
library(knitr)
library(tidyr)
library(RODBC) 
library(DT)


options(scipen=6, stringsAsFactors = F)

lang <- getOption("highcharter.lang")
lang$thousandsSep <-  ","
options(highcharter.lang = lang)

security <- read.csv("databasePass.csv", header = T)


my_server <- "192.168.1.11"
my_db <- "tessa_db"

db <- odbcDriverConnect(paste0("DRIVER={SQL Server};
                              server=",my_server,";
                              database=",my_db,";
                              uid=",security$UserName[1],";
                              pwd=",security$Password[1]))


report_query_all_pats <-  paste0("select count(distinct patient_id) from tessa_db.dbo.bics_patients;")
all_pats_after_sept_2020 <- sqlQuery(db, report_query_all_pats)

report_data_query_2020 <- paste0("SELECT * FROM tessa_db.dbo.all_pats_march2020 where copd_diag is not null and copd_resolved is null;")
all_pats_2020 <- sqlQuery(db, report_data_query_2020) %>% distinct()

report_data_query_2019 <- paste0("SELECT * FROM tessa_db.dbo.all_pats_march2019 where copd_diag is not null and copd_resolved is null;")
all_pats_2019 <- sqlQuery(db, report_data_query_2019) %>% distinct()

report_data_query_2019 <- paste0("SELECT * FROM tessa_db.dbo.all_pats_march2018 where copd_diag is not null and copd_resolved is null;")
all_pats_2018 <- sqlQuery(db, report_data_query_2019) %>%  distinct()


total_pats <- length(unique(all_pats_2019$patient_id))
total_practices <- length(unique(all_pats_2019$practice_id))
```

# Purpose 

The following is a report comparing COPD patients EMR recorded exacerbations from March - September 2018, March - September 2019 and March - September 2020. The population was restricted to `r paste0("<b>", format(total_pats, big.mark = ','), "</b>")` patients from `r paste0("<b>", format(total_practices, big.mark = ','), "</b>")` practices that had an audit date after Sept. 2020.


---

\newpage

# Population Selection 

```{r patientBreakdown, fig.height = 3, fig.align='center'}
library(DiagrammeR)

# total number of exacerbations march 2019-2020 - all pats: 358883
# total number of freq exac pats march 2019-2020 - all pats: 28434
# total number of freq exac pats march 2019-2020 - all pats: 28434

after_sept <- 345504
total_exac_march <- 358883
total_exac_march_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_total > 0),])
total_exac_march_2019 <- nrow(all_pats_2020[(all_pats_2019$exacb_total > 0),])
total_exac_march_2018 <- nrow(all_pats_2020[(all_pats_2018$exacb_total > 0),])

freq_exac_pats <- 25649
freq_exac_pats_exac_total <- 261629



d <- c(A1 = paste0("<b>Total Asthma/COPD Patients with Audit Date after Sept. 2020:       <font color = '#548235'>",
                   format(all_pats_after_sept_2020,big.mark = ','),"</font></b>"),
       A = paste("<b>COPD Patients:      <font color = 'white'>", format(total_pats, big.mark = ','), 
                  "</font></b>"),
       P = paste("<b>Total Patients with at least 1 Exacerbation:     <font color = 'white'>", format(total_exac_march_2020, big.mark = ','),  "</font></b><br/><br/><font point-size = '9pt'>from March - Sept. 2020</font>"),
       P = paste("<b>Total Patients with at least 1 Exacerbation:     <font color = 'white'>", format(total_exac_march_2019, big.mark = ','),  "</font></b><br/><br/><font point-size = '9pt'>from March - Sept. 2019</font>"),
       P = paste("<b>Total Patients with at least 1 Exacerbation:     <font color = 'white'>", format(total_exac_march_2018, big.mark = ','),  "</font></b><br/><br/><font point-size = '9pt'>from March - Sept. 2018</font>"),
       filler = '        ')



  
graphText <- "
    digraph SampleFiltering {

        node [shape = octogon,
        fontname = Helvetica,
        width = 2, 
        style = filled,
        penwidth = 2,
        color = '#D5E3F0']
        Total; 
        
        node [shape = box,
        fontname = Helvetica,
        width = 2,
        style = filled,
        penwidth = 2,
        color = '#FFA977']
        Asthma; 

        
        node [shape = box,
        fontname = Helvetica,
        width = 2,
        style = filled,
        penwidth = 2,
        minlen = 3,
        color = '#0D5295']
        Exacerbations_2020;
        
        
        node [shape = box,
        fontname = Helvetica,
        width = 2,
        style = filled,
        penwidth = 2,
        minlen = 3,
        color = '#9EB9D4']
        Exacerbations_2019;
        
        
        node [shape = box,
        fontname = Helvetica,
        width = 2,
        style = filled,
        penwidth = 2,
        minlen = 3,
        color = '#FFA977']
        Exacerbations_2018;
        
        # edge statements
        Total->Asthma
        {rank=same ; Asthma->Exacerbations_2020}
        Exacerbations_2020->Exacerbations_2019
        Exacerbations_2019->Exacerbations_2018

        Total [label = <@@1-1>]
        Asthma [label = <@@1-2>]
        Exacerbations_2020 [label = <@@1-3>]
        Exacerbations_2019 [label = <@@1-4>]
        Exacerbations_2018 [label = <@@1-5>]
       

    }


"

graphText <- gsub('@@1-1', d[1], graphText)
graphText <- gsub('@@1-2', d[2], graphText)
graphText <- gsub('@@1-3', d[3], graphText)
graphText <- gsub('@@1-4', d[4], graphText)
graphText <- gsub('@@1-5', d[5], graphText)


grViz(graphText)  
  
```

---

\newpage

# Overall Exacerbation Rates

Exacerbation rates were comapred using patient's EMR looking at March - September 2018, March - September 2019 and March - September 2020. These are split into 3 categories, each containing patients that have had <b>at least 1 of the following</b>:

* COPD exacerbation 
  + Explicit COPD coded exacerbation 
  + Acute OCS prescription
  + Hospital admission 


```{r all_exac}
ocs_exac_total_ehr_2020 <- nrow(all_pats_2020[(all_pats_2020$ocs_acute > 0),])
ha_exac_total_ehr_2020 <- nrow(all_pats_2020[(all_pats_2020$hosp_admit > 0),])
copd_exac_totalehr_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd > 0),])
copd_exac_codes_totalehr_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd_codes > 0),])

ocs_exac_total_ehr_2019 <- nrow(all_pats_2019[(all_pats_2019$ocs_acute > 0),])
ha_exac_total_ehr_2019 <- nrow(all_pats_2019[(all_pats_2019$hosp_admit > 0),])
copd_exac_totalehr_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd > 0),])
copd_exac_codes_totalehr_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd_codes > 0),])

ocs_exac_total_ehr_2018 <- nrow(all_pats_2018[(all_pats_2018$ocs_acute > 0),])
ha_exac_total_ehr_2018 <- nrow(all_pats_2018[(all_pats_2018$hosp_admit > 0),])
copd_exac_totalehr_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd > 0),])
copd_exac_codes_totalehr_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd_codes > 0),])


exac_all_2020 <- data.frame(y = round(c(copd_exac_totalehr_2020,
                                   copd_exac_codes_totalehr_2020,
                                   ocs_exac_total_ehr_2020,
                                   ha_exac_total_ehr_2020)/total_pats*100,1),
                                  count = format(c(copd_exac_totalehr_2020,
                                   copd_exac_codes_totalehr_2020,
                                   ocs_exac_total_ehr_2020,
                                   ha_exac_total_ehr_2020), big.mark = ',')) %>% 
  mutate(y = as.numeric(y), pointWidth = c(90, 40, 40, 40))

exac_all_2019 <- data.frame(y = round(c(copd_exac_totalehr_2019,
                                        copd_exac_codes_totalehr_2019,
                                        ocs_exac_total_ehr_2019,
                                        ha_exac_total_ehr_2019)/total_pats*100,1),
                            count = format(c(copd_exac_totalehr_2019,
                                             copd_exac_codes_totalehr_2019,
                                             ocs_exac_total_ehr_2019,
                                             ha_exac_total_ehr_2019), big.mark = ',')) %>% 
  mutate(y = as.numeric(y), pointWidth = c(90, 40, 40, 40))

exac_all_2018 <- data.frame(y = round(c(copd_exac_totalehr_2018,
                                        copd_exac_codes_totalehr_2018,
                                        ocs_exac_total_ehr_2018,
                                        ha_exac_total_ehr_2018)/total_pats*100,1),
                            count = format(c(copd_exac_totalehr_2018,
                                        copd_exac_codes_totalehr_2018,
                                        ocs_exac_total_ehr_2018,
                                        ha_exac_total_ehr_2018), big.mark = ',')) %>% 
  mutate(y = as.numeric(y), pointWidth = c(90, 40, 40, 40))





library(highcharter)
total_exac <- highchart() %>%
  hc_chart(type = 'column') %>%
  hc_xAxis(type="category", title = list(text = 'Exacerbation Rate Comparison'), labels = list(useHTML = T), 
           categories = c('COPD Exacerbation',  
                          'Explicit COPD Exacerbation Code', 
                          'Acute OCS Prescription', 'Hospital Admission')) %>%
  hc_plotOptions(series = list(groupPadding = 0.2, pointPadding = -.4)) %>%
  hc_add_series(name = "March - Sept. 2018", data =  exac_all_2018, useHTML = T,
                color = '#FFA977')%>%
  hc_add_series(name = "March - Sept. 2019", data =  exac_all_2019, useHTML = T,
                color = '#9EB9D4') %>%
  hc_add_series(name = "March - Sept. 2020", data =  exac_all_2020, useHTML = T,
                color = '#0D5295') %>%
  hc_tooltip(pointFormat = paste('<b>{series.name}</b><br/><b>Percent of Pop</b>:{point.y}%<br/><b>Count</b>: {point.count}<br/><b>Total Populaiton</b>:52,863'), 
             useHTML = T)  %>%
  hc_yAxis(labels = list(format = "{value}%"), tickInterval = 5)%>%
  hc_size(height = 400)

total_exac
```


\newpage

The average and standard deviation has also been caluculated for these categories.


```{r mrcTable}
# ocs
avg_copd_2020 <- mean(all_pats_2020$exacb_copd)
avg_ocs_2020 <- mean(all_pats_2020$ocs_acute)
avg_ha_2020 <- mean(all_pats_2020$hosp_admit)
avg_gen_2020 <- mean(all_pats_2020$exacb_copd_codes)

avg_copd_2019 <- mean(all_pats_2019$exacb_copd)
avg_ocs_2019 <- mean(all_pats_2019$ocs_acute)
avg_ha_2019 <- mean(all_pats_2019$hosp_admit)
avg_gen_2019 <- mean(all_pats_2019$exacb_copd_codes)

avg_copd_2018 <- mean(all_pats_2018$exacb_copd)
avg_ocs_2018 <- mean(all_pats_2018$ocs_acute)
avg_ha_2018 <- mean(all_pats_2018$hosp_admit)
avg_gen_2018 <- mean(all_pats_2018$exacb_copd_codes)


sd_copd_2020 <- sd(all_pats_2020$exacb_copd)
sd_ocs_2020 <- sd(all_pats_2020$ocs_acute)
sd_ha_2020 <- sd(all_pats_2020$hosp_admit)
sd_gen_2020 <- sd(all_pats_2020$exacb_copd_codes)

sd_copd_2019 <- sd(all_pats_2019$exacb_copd)
sd_ocs_2019 <- sd(all_pats_2019$ocs_acute)
sd_ha_2019 <- sd(all_pats_2019$hosp_admit)
sd_gen_2019 <- sd(all_pats_2019$exacb_copd_codes)

sd_copd_2018 <- sd(all_pats_2018$exacb_copd)
sd_ocs_2018 <- sd(all_pats_2018$ocs_acute)
sd_ha_2018 <- sd(all_pats_2018$hosp_admit)
sd_gen_2018 <- sd(all_pats_2018$exacb_copd_codes)

sd <- data.frame(measure = c('COPD Exacerbation', 'Acute OCS', 'Hospital Admissions', 'Explicit COPD Exacerbation Code'), 
                 avg2020 = round(c(avg_copd_2020, avg_ocs_2020, avg_ha_2020, avg_gen_2020), digits = 2), 
                 avg2019 = round(c(avg_copd_2019, avg_ocs_2019, avg_ha_2019, avg_gen_2019), digits = 2),
                 avg2018 = round(c(avg_copd_2018, avg_ocs_2018, avg_ha_2018, avg_gen_2018), digits = 2),
                 sd_2020 = round(c(sd_copd_2020, sd_ocs_2020, sd_ha_2020, sd_gen_2020), digits = 2), 
                 sd_2019 = round(c(sd_copd_2019, sd_ocs_2019, sd_ha_2019, sd_gen_2019), digits = 2),
                 sd_2018 = round(c(sd_copd_2018, sd_ocs_2018, sd_ha_2018, sd_gen_2018), digits = 2))


colnames(sd)[1] <- 'Measure'
colnames(sd)[2] <- 'March - Sept. 2020 Average'
colnames(sd)[3] <- 'March - Sept. 2019 Average'
colnames(sd)[4] <- 'March - Sept. 2018 Average'
colnames(sd)[5] <- 'March - Sept. 2020 Standard Deviation'
colnames(sd)[6] <- 'March - Sept. 2019 Standard Deviation'
colnames(sd)[7] <- 'March - Sept. 2018 Standard Deviation'

kable(sd, "html", escape = F, align = "l", booktab = T) %>%
  row_spec(0, background = '#a9a9a9')


```

---

\newpage

# COPD Exacerbation Rates

This section breaks down the total number of COPD exacerbations by frequency.

```{r copd_exac}
copd_exac_0_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd == 0),])
copd_exac_1_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd == 1),])
copd_exac_2_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd == 2),])
copd_exac_3p_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd > 2),])

emr_copd_2020 <- data.frame(y = round(c(copd_exac_0_2020, 
                                                    copd_exac_1_2020, 
                                                     copd_exac_2_2020, 
                                                     copd_exac_3p_2020)/total_pats*100,1),
                                     count = format(c(copd_exac_0_2020, 
                                                    copd_exac_1_2020, 
                                                     copd_exac_2_2020, 
                                                     copd_exac_3p_2020), big.mark = ','))

copd_exac_0_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd == 0),])
copd_exac_1_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd == 1),])
copd_exac_2_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd == 2),])
copd_exac_3p_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd > 2),])

emr_copd_2019 <- data.frame(y = round(c(copd_exac_0_2019, 
                                          copd_exac_1_2019, 
                                          copd_exac_2_2019, 
                                          copd_exac_3p_2019)/total_pats*100,1),
                              count = format(c(copd_exac_0_2019, 
                                          copd_exac_1_2019, 
                                          copd_exac_2_2019, 
                                          copd_exac_3p_2019), big.mark = ','))

copd_exac_0_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd == 0),])
copd_exac_1_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd == 1),])
copd_exac_2_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd == 2),])
copd_exac_3p_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd > 2),])


exac0_copd <- data.frame(y = c(copd_exac_0_2020, copd_exac_0_2019, copd_exac_0_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac1_copd <- data.frame(y = c(copd_exac_1_2020, copd_exac_1_2019, copd_exac_1_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac2_copd <- data.frame(y = c(copd_exac_2_2020, copd_exac_2_2019, copd_exac_2_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac3p_copd <- data.frame(y = c(copd_exac_3p_2020, copd_exac_3p_2019, copd_exac_3p_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))


library(highcharter)
copd_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F)))) %>%
  hc_add_series(name = "3+ Exacerbations", data = exac3p_copd, color = '#E26F2D')%>%
   hc_add_series(name = "2 Exacerbations", data = exac2_copd, color = '#FFA977')%>%
  hc_add_series(name = "1 Exacerbation", data = exac1_copd, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Exacerbations", data = exac0_copd, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5)%>%
  hc_size(height = 400) 


copd_exac
```


---

\newpage

## Explicit Code for COPD Exacerbations

The following sections break down the frequencies of each of the total number of asthma exacerbations parts: explicit coding, acute OCS, and hospital admissions.

```{r copd_codes_exac}
copd_codes_exac_0_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd_codes == 0),])
copd_codes_exac_1_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd_codes == 1),])
copd_codes_exac_2_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd_codes == 2),])
copd_codes_exac_3p_2020 <- nrow(all_pats_2020[(all_pats_2020$exacb_copd_codes > 2),])

emr_copd_codes_2020 <- data.frame(y = round(c(copd_codes_exac_0_2020, 
                                                    copd_codes_exac_1_2020, 
                                                     copd_codes_exac_2_2020, 
                                                     copd_codes_exac_3p_2020)/total_pats*100,1),
                                     count = format(c(copd_codes_exac_0_2020, 
                                                    copd_codes_exac_1_2020, 
                                                     copd_codes_exac_2_2020, 
                                                     copd_codes_exac_3p_2020), big.mark = ','))

copd_codes_exac_0_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd_codes == 0),])
copd_codes_exac_1_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd_codes == 1),])
copd_codes_exac_2_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd_codes == 2),])
copd_codes_exac_3p_2019 <- nrow(all_pats_2019[(all_pats_2019$exacb_copd_codes > 2),])

emr_copd_codes_2019 <- data.frame(y = round(c(copd_codes_exac_0_2019, 
                                          copd_codes_exac_1_2019, 
                                          copd_codes_exac_2_2019, 
                                          copd_codes_exac_3p_2019)/total_pats*100,1),
                              count = format(c(copd_codes_exac_0_2019, 
                                          copd_codes_exac_1_2019, 
                                          copd_codes_exac_2_2019, 
                                          copd_codes_exac_3p_2019), big.mark = ','))

copd_codes_exac_0_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd_codes == 0),])
copd_codes_exac_1_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd_codes == 1),])
copd_codes_exac_2_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd_codes == 2),])
copd_codes_exac_3p_2018 <- nrow(all_pats_2018[(all_pats_2018$exacb_copd_codes > 2),])


exac0_copd_codes <- data.frame(y = c(copd_codes_exac_0_2020, copd_codes_exac_0_2019, copd_codes_exac_0_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac1_copd_codes <- data.frame(y = c(copd_codes_exac_1_2020, copd_codes_exac_1_2019, copd_codes_exac_1_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac2_copd_codes <- data.frame(y = c(copd_codes_exac_2_2020, copd_codes_exac_2_2019, copd_codes_exac_2_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac3p_copd_codes <- data.frame(y = c(copd_codes_exac_3p_2020, copd_codes_exac_3p_2019 , copd_codes_exac_3p_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))


library(highcharter)
copd_codes_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F)))) %>%
  hc_add_series(name = "3+ Exacerbations", data = exac3p_copd_codes, color = '#E26F2D')%>%
   hc_add_series(name = "2 Exacerbations", data = exac2_copd_codes, color = '#FFA977')%>%
  hc_add_series(name = "1 Exacerbation", data = exac1_copd_codes, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Exacerbations", data = exac0_copd_codes, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5) %>%
  hc_size(height = 400)

copd_codes_exac
```


---

\newpage

## Acute OCS Prescriptions


```{r ocs_exac}
ocs_exac_0_2020 <- nrow(all_pats_2020[(all_pats_2020$ocs_acute == 0),])
ocs_exac_1_2020 <- nrow(all_pats_2020[(all_pats_2020$ocs_acute == 1),])
ocs_exac_2_2020 <- nrow(all_pats_2020[(all_pats_2020$ocs_acute == 2),])
ocs_exac_3p_2020 <- nrow(all_pats_2020[(all_pats_2020$ocs_acute > 2),])

ocs_2020 <- data.frame(y = round(c(ocs_exac_0_2020, 
                                                ocs_exac_1_2020, 
                                                ocs_exac_2_2020, 
                                                ocs_exac_3p_2020)/total_pats*100,1),
                                  count = format(c(ocs_exac_0_2020, 
                                                ocs_exac_1_2020, 
                                                ocs_exac_2_2020, 
                                                ocs_exac_3p_2020), big.mark = ','))

ocs_exac_0_2019 <- nrow(all_pats_2019[(all_pats_2019$ocs_acute == 0),])
ocs_exac_1_2019 <- nrow(all_pats_2019[(all_pats_2019$ocs_acute == 1),])
ocs_exac_2_2019 <- nrow(all_pats_2019[(all_pats_2019$ocs_acute == 2),])
ocs_exac_3p_2019 <- nrow(all_pats_2019[(all_pats_2019$ocs_acute > 2),])

ocs_2019 <- data.frame(y = round(c(ocs_exac_0_2019, 
                                   ocs_exac_1_2019, 
                                   ocs_exac_2_2019, 
                                   ocs_exac_3p_2019)/total_pats*100,1),
                       count = format(c(ocs_exac_0_2019, 
                                        ocs_exac_1_2019, 
                                        ocs_exac_2_2019, 
                                        ocs_exac_3p_2019), big.mark = ','))

ocs_exac_0_2018 <- nrow(all_pats_2018[(all_pats_2018$ocs_acute == 0),])
ocs_exac_1_2018 <- nrow(all_pats_2018[(all_pats_2018$ocs_acute == 1),])
ocs_exac_2_2018 <- nrow(all_pats_2018[(all_pats_2018$ocs_acute == 2),])
ocs_exac_3p_2018 <- nrow(all_pats_2018[(all_pats_2018$ocs_acute > 2),])

exac0_ocs <- data.frame(y = c(ocs_exac_0_2020, ocs_exac_0_2019, ocs_exac_0_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac1_ocs <- data.frame(y = c(ocs_exac_1_2020, ocs_exac_1_2019, ocs_exac_1_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac2_ocs <- data.frame(y = c(ocs_exac_2_2020, ocs_exac_2_2019, ocs_exac_2_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac3p_ocs <- data.frame(y = c(ocs_exac_3p_2020, ocs_exac_3p_2019, ocs_exac_3p_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))


library(highcharter)
ocs_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F)))) %>%
  hc_add_series(name = "3+ Acute OCS Prescriptions", data = exac3p_ocs, color = '#E26F2D')%>%
   hc_add_series(name = "2 Acute OCS Prescriptions", data = exac2_ocs, color = '#FFA977')%>%
  hc_add_series(name = "1 Acute OCS Prescription", data = exac1_ocs, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Acute OCS Prescriptions", data = exac0_ocs, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5)%>%
  hc_size(height = 400)

ocs_exac
```

---

\newpage

## Hosptial Admissions


```{r ha_exac}
ha_exac_0_2020 <- nrow(all_pats_2020[(all_pats_2020$hosp_admit == 0),])
ha_exac_1_2020 <- nrow(all_pats_2020[(all_pats_2020$hosp_admit == 1),])
ha_exac_2_2020 <- nrow(all_pats_2020[(all_pats_2020$hosp_admit == 2),])
ha_exac_3p_2020 <- nrow(all_pats_2020[(all_pats_2020$hosp_admit > 2),])


ha_2020 <- data.frame(y = round(c(ha_exac_0_2020, 
                                              ha_exac_1_2020, 
                                              ha_exac_2_2020, 
                                              ha_exac_3p_2020)/total_pats*100,1),
                                    count = format(c(ha_exac_0_2020, 
                                              ha_exac_1_2020, 
                                              ha_exac_2_2020, 
                                              ha_exac_3p_2020), big.mark = ','))

ha_exac_0_2019 <- nrow(all_pats_2019[(all_pats_2019$hosp_admit == 0),])
ha_exac_1_2019 <- nrow(all_pats_2019[(all_pats_2019$hosp_admit == 1),])
ha_exac_2_2019 <- nrow(all_pats_2019[(all_pats_2019$hosp_admit == 2),])
ha_exac_3p_2019 <- nrow(all_pats_2019[(all_pats_2019$hosp_admit > 2),])


ha_2019 <- data.frame(y = round(c(ha_exac_0_2019, 
                                  ha_exac_1_2019, 
                                  ha_exac_2_2019, 
                                  ha_exac_3p_2019)/total_pats*100,1),
                      count = format(c(ha_exac_0_2019, 
                                       ha_exac_1_2019, 
                                       ha_exac_2_2019, 
                                       ha_exac_3p_2019), big.mark = ','))

ha_exac_0_2018 <- nrow(all_pats_2018[(all_pats_2018$hosp_admit == 0),])
ha_exac_1_2018 <- nrow(all_pats_2018[(all_pats_2018$hosp_admit == 1),])
ha_exac_2_2018 <- nrow(all_pats_2018[(all_pats_2018$hosp_admit == 2),])
ha_exac_3p_2018 <- nrow(all_pats_2018[(all_pats_2018$hosp_admit > 2),])

exac0_ha <- data.frame(y = c(ha_exac_0_2020, ha_exac_0_2019, ha_exac_0_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac1_ha <- data.frame(y = c(ha_exac_1_2020, ha_exac_1_2019, ha_exac_1_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac2_ha <- data.frame(y = c(ha_exac_2_2020, ha_exac_2_2019, ha_exac_2_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))
exac3p_ha <- data.frame(y = c(ha_exac_3p_2020, ha_exac_3p_2019, ha_exac_3p_2018), 
                      category = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018'))


library(highcharter)
ha_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('March - Sept. 2020', 'March - Sept. 2019', 'March - Sept. 2018')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F)))) %>%
  hc_add_series(name = "3+ Hospital Admissions", data = exac3p_ha, color = '#E26F2D')%>%
   hc_add_series(name = "2 Hospital Admissions", data = exac2_ha, color = '#FFA977')%>%
  hc_add_series(name = "1 Hospital Admission", data = exac1_ha, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Hospital Admissions", data = exac0_ha, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5) %>%
  hc_size(height = 400)


ha_exac
```