---
title: "Exacerbation Rates Comparison: Questionnaire vs. EMR - COPD Patients"
author: 
-  Tessa LiVoti
output:
  rmdformats::readthedown:
    number_sections: true
    highlight: kate
    mathjax: false
    use_bookdown: true
    cards: true
    css: custom.css
    toc_float: true
      
---

<style type="text/css">
.main-container {
  max-width: 1000px !important;
  margin-left: auto;
  margin-right: auto;
}
div.rect {
  border: 2px solid #cb6328;
  border-radius: 15px;
  padding: 10px;
}
</style>

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F, comment="", fig.height=5, fig.pos='H')
library(highcharter)
library(htmlwidgets)
library(kableExtra)
library(htmltools)
library(lubridate)
library(ggplot2)
library(dplyr)
library(Hmisc)
library(knitr)
library(tidyr)
library(RODBC) 
library(DT)
library(plotrix) # for std.error function

options(scipen=6, stringsAsFactors = F)

lang <- getOption("highcharter.lang")
lang$thousandsSep <-  ","
options(highcharter.lang = lang)

security <- read.csv("databasePass.csv", header = T)


my_server <- "192.168.1.11"
my_db <- "tessa_db"

db <- odbcDriverConnect(paste0("DRIVER={SQL Server};
                              server=",my_server,";
                              database=",my_db,";
                              uid=",security$UserName[1],";
                              pwd=",security$Password[1]))
# pull only covid19 exac questions
questionnaire_pats <- sqlQuery(db, "select r.*, q.event_date from opcdw.dbo.f_quest_responses r inner join opcdw.dbo.f_quest_questionnaires q 
                               on r.questionnaire_id = q.questionnaire_id and r.opc_patient_id = q.opc_patient_id where question_id = '121' 
                               or question_id = '122' or question_id = '123'")
questionnaire_pats <- questionnaire_pats %>% 
  mutate(quest_patient_id =  paste0("'", opc_patient_id, "'")) 
questionnaire_pats1 <- paste0(questionnaire_pats$quest_patient_id, collapse = ",")  

report_data_query <- paste0("SELECT * FROM reports.dbo.opc_audit_patients where patient_id in (", questionnaire_pats1, ");")
all_pats1 <- sqlQuery(db, report_data_query) %>% filter(!is.na(copd_diag) & is.na(copd_resolved)) %>% distinct()
all_pats2 <- all_pats1 %>% select(c(patient_id)) %>% mutate(ehr = 1)

questionnaire_pats <- questionnaire_pats %>% 
  left_join(all_pats2, by = c("opc_patient_id" = "patient_id")) %>% 
  filter(ehr == 1) %>% 
  distinct()

total_pats <- length(unique(questionnaire_pats$opc_patient_id))
```

# Purpose 

The following is a report comparing a patients reported exacerbations vs. what is recorded in their EMR from Sept. 2019- Sept 2020. The population was restricted to <b>207 patients</b> from <b>5 practices</b> meeting the following criteria:

* Had an audit date after Sept. 1, 2020.
* Questionnaire data on exacerbations. 
* Reported COPD on questionnaire

---

# EMR vs. Questionnaire exacerbation rates

Comparing exacerbation rates using patient's EMR versus their Questionnaire answers. These are split into 3 categories, each containing patients that have had/reported at least 1 exacerbation in the following. 

* Acute OCS Rrescriptions
* Hopsital Admissions 
* General Exacerbation Code


```{r all_exac}
ocs_exac_total_ehr <- nrow(all_pats1[(all_pats1$ocs_acute > 0),])
ha_exac_total_ehr <- nrow(all_pats1[(all_pats1$hosp_admit > 0),])
gen_exac_total_ehr <- nrow(all_pats1[(all_pats1$exacb_tot_codes > 0),])

ocs_exac_total_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 121 & questionnaire_pats$response > 0),])
ha_exac_total_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 122 & questionnaire_pats$response > 0),])
gen_exac_total_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 123 & questionnaire_pats$response > 0),])

ocs_acute_quest <- filter(questionnaire_pats, question_id == 121) 

hosp_admit_quest <- filter(questionnaire_pats, question_id == 122)

gen_quest <- filter(questionnaire_pats, question_id == 123)


emr_exac <- data.frame(y = round(c(ocs_exac_total_ehr, 
                                                ha_exac_total_ehr, 
                                                gen_exac_total_ehr)/total_pats*100,1),
                                  count = format(c(ocs_exac_total_ehr, 
                                                ha_exac_total_ehr, 
                                                gen_exac_total_ehr), big.mark = ','))

quest_exac <- data.frame(y = round(c(ocs_exac_total_q, 
                                                 ha_exac_total_q, 
                                                 gen_exac_total_q)/total_pats*100,1), 
                                   count = format(c(ocs_exac_total_q, 
                                                 ha_exac_total_q, 
                                                 gen_exac_total_q), 
                                                  big.mark = ','))


library(highcharter)
total_exac <- highchart() %>%
  hc_chart(type = 'column') %>%
  hc_xAxis(type="category", title = list(text = 'Exacerbation rate comparison'), labels = list(useHTML = T), 
           categories = c('Acute OCS Prescription', 'Hospital Admissions', 'General Exacerbation')) %>%
  hc_plotOptions(series = list(groupPadding = 0.2, pointPadding = -.4)) %>%
  hc_add_series(name = "Questionnaire", data = quest_exac, useHTML = T,
                color = '#9EB9D4') %>% 
  hc_add_series(name = "EMR", data =  emr_exac, useHTML = T,
                color = '#0D5295') %>%
  hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Percent of Pop</b>:{point.y}%<br/><b>Count</b>: {point.count}', 
             useHTML = T)  %>%
  hc_yAxis(labels = list(format = "{value}%"), tickInterval = 5)

total_exac
```
Below are the standard error and average for each categorey. The following formula has been used for the standard error with Q being quesitonnaire answer and E being a patient's recorded EMR exacerbation. 

<div class = "row", style = "display:flex; align-items:center;">
<div style="float:left; width:35%;">
$$SE = \sqrt{\frac{\sum(Q-E)^2}{N-2}}$$


</div> 

<div style="float:left; width:50%;">
```{r mrcTable}
# ocs
ocs_acute_q <- filter(questionnaire_pats, question_id == 121) %>% 
  mutate(exac_type = 'Acute OCS Prescription') %>% 
  select(c(opc_patient_id, exac_type, response))%>% 
  rename(patient_id = opc_patient_id, 
         response_q = response) %>% 
  filter(response_q < 350)
ocs_acute_ehr <- all_pats1 %>% 
  mutate(exac_type = 'Acute OCS Prescription') %>% 
  select(c(patient_id, exac_type, ocs_acute))%>% 
  rename(response_ehr = ocs_acute)

sd_ocs <- left_join(ocs_acute_ehr, ocs_acute_q, by = c('patient_id', 'exac_type')) %>% 
  distinct(patient_id, exac_type, .keep_all = T) 
sd_ocs <- sd_ocs %>% 
  mutate(
    y_sub_yprime = response_q - response_ehr
  ) %>% 
  mutate(
    y_sub_yprime_sq = (y_sub_yprime)^2
  )

hosp_admit_q <- filter(questionnaire_pats, question_id == 122)%>% 
  mutate(exac_type = 'Hospital Admission') %>% 
  select(c(opc_patient_id, exac_type, response))%>% 
  rename(patient_id = opc_patient_id, 
         response_q = response)
hosp_admit_ehr <- all_pats1 %>% 
  mutate(exac_type = 'Hospital Admission') %>% 
  select(c(patient_id, exac_type, hosp_admit))%>% 
  rename(response_ehr = hosp_admit)

sd_ha <- left_join(hosp_admit_ehr, hosp_admit_q, by = c('patient_id', 'exac_type')) %>% 
  distinct(patient_id, exac_type, .keep_all = T)%>%  
  mutate(
    y_sub_yprime = response_q - response_ehr
  ) %>% 
  mutate(
    y_sub_yprime_sq = (y_sub_yprime)^2
  )

gen_q <- filter(questionnaire_pats, question_id == 123)%>% 
  mutate(exac_type = 'General exacerbation') %>% 
  select(c(opc_patient_id, exac_type, response)) %>% 
  rename(patient_id = opc_patient_id, 
         response_q = response) %>% 
  filter(response_q < 500)
gen_ehr <- all_pats1 %>% 
  mutate(exac_type = 'General exacerbation') %>% 
  select(c(patient_id, exac_type, exacb_tot_codes)) %>% 
  rename(response_ehr = exacb_tot_codes)
sd_gen <- left_join(gen_ehr, gen_q, by = c('patient_id', 'exac_type')) %>% 
  distinct(patient_id, exac_type, .keep_all = T)%>% 
  mutate(
    y_sub_yprime = response_q - response_ehr
  ) %>% 
  mutate(
    y_sub_yprime_sq = (y_sub_yprime)^2
  )

sd_ocs1 <- sqrt(sum(sd_ocs$y_sub_yprime_sq, na.rm = T)/(length(unique(sd_ocs$patient_id))-2))
sd_ha1 <- sqrt(sum(sd_ha$y_sub_yprime_sq, na.rm = T)/(length(unique(sd_ha$patient_id))-2))
sd_gen1 <- sqrt(sum(sd_gen$y_sub_yprime_sq, na.rm = T)/(length(unique(sd_gen$patient_id))-2))

avg_ocs_emr <- mean(ocs_acute_ehr$response_ehr)
avg_ha_emr <- mean(hosp_admit_ehr$response_ehr)
avg_gen_emr <- mean(gen_ehr$response_ehr)

avg_ocs_q <- mean(ocs_acute_q$response_q, na.rm = T)
avg_ha_q <- mean(hosp_admit_q$response_q, na.rm = T)
avg_gen_q <- mean(gen_q$response_q, na.rm = T)

sd <- data.frame(measure = c('Acute OCS', 'Hospital Admissions', 'General Exacerbation'), 
                 emr_avg = c(avg_ocs_emr, avg_ha_emr, avg_gen_emr), 
                 q_avg = c(avg_ocs_q, avg_ha_q, avg_gen_q),
                  ha_sd = c(sd_ocs1, sd_ha1, sd_gen1))


colnames(sd)[1] <- 'Measure'
colnames(sd)[2] <- 'EMR Average'
colnames(sd)[3] <- 'Questionnaire Average'
colnames(sd)[4] <- 'Standard Error'

kable(sd, "html", escape = F, align = "l", booktab = T) %>%
  row_spec(0, background = '#a9a9a9')


```

</div> 
</div> 

---

# Acute OCS 

This section breaks down each categorey by frequency followed by a scatter plot, including a regression line, plotting a patient's EMR recorded exacerbation against their Questionnaire reported exacerbations.

```{r ocs_exac}
ocs_exac_0_ehr <- nrow(all_pats1[(all_pats1$ocs_acute == 0),])
ocs_exac_1_ehr <- nrow(all_pats1[(all_pats1$ocs_acute == 1),])
ocs_exac_2_ehr <- nrow(all_pats1[(all_pats1$ocs_acute == 2),])
ocs_exac_3p_ehr <- nrow(all_pats1[(all_pats1$ocs_acute > 2),])

ocs_exac_0_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 121 & questionnaire_pats$response == 0),])
ocs_exac_1_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 121 & questionnaire_pats$response == 1),])
ocs_exac_2_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 121 & questionnaire_pats$response == 2),])
ocs_exac_3p_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 121 & questionnaire_pats$response > 2),])

emr_ocs <- data.frame(y = round(c(ocs_exac_0_ehr, 
                                                ocs_exac_1_ehr, 
                                                ocs_exac_2_ehr, 
                                                ocs_exac_3p_ehr)/total_pats*100,1),
                                  count = format(c(ocs_exac_0_ehr, 
                                                ocs_exac_1_ehr, 
                                                ocs_exac_2_ehr, 
                                                ocs_exac_3p_ehr), big.mark = ','))

quest_ocs <- data.frame(y = round(c(ocs_exac_0_q, 
                                                 ocs_exac_1_q, 
                                                 ocs_exac_2_q, 
                                                 ocs_exac_3p_q)/total_pats*100,1), 
                                   count = format(c(ocs_exac_0_q, 
                                                 ocs_exac_1_q, 
                                                 ocs_exac_2_q, 
                                                 ocs_exac_3p_q), 
                                                  big.mark = ','))

exac0_ocs <- data.frame(y = c(ocs_exac_0_q, ocs_exac_0_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac1_ocs <- data.frame(y = c(ocs_exac_1_q, ocs_exac_1_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac2_ocs <- data.frame(y = c(ocs_exac_2_q, ocs_exac_2_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac3p_ocs <- data.frame(y = c(ocs_exac_3p_q, ocs_exac_3p_ehr), 
                      category = c('Questionnaire', 'EMR'))


library(highcharter)
ocs_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('Questionnaire', 'EMR')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F))))  %>%
  hc_add_series(name = "3+ Acute OCS Prescriptions", data = exac3p_ocs, color = '#E26F2D')%>%
   hc_add_series(name = "2 Acute OCS Prescriptions", data = exac2_ocs, color = '#FFA977')%>%
  hc_add_series(name = "1 Acute OCS Prescription", data = exac1_ocs, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Acute OCS Prescriptions", data = exac0_ocs, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5) 

ocs_exac
```

---

## Acute OCS Breakdown

```{r ocs_exac_scatter, message=FALSE, warning=FALSE}
ocs_acute_q <- filter(questionnaire_pats, question_id == 121) %>% 
  mutate(exac_type = 'Acute OCS Prescription') %>% 
  select(c(opc_patient_id, exac_type, response))%>% 
  rename(patient_id = opc_patient_id, 
         response_q = response) 


ocs_acute_ehr <- all_pats1 %>% 
  mutate(exac_type = 'Acute OCS Prescription') %>% 
  select(c(patient_id, exac_type, ocs_acute))%>% 
  rename(response_ehr = ocs_acute)

exac_scatter_test <- left_join(ocs_acute_ehr, ocs_acute_q, by = c('patient_id', 'exac_type')) %>% 
  distinct(patient_id, exac_type, .keep_all = T)

hchart(exac_scatter_test, "point", hcaes(response_ehr, response_q), regression = TRUE) %>% 
  hc_colors(c("#d35400", "#2980b9", "#2ecc71")) %>% 
  hc_add_dependency("plugins/highcharts-regression.js") %>% 
  hc_xAxis(title = list(text = 'EMR Responses'), labels = list(useHTML = T), max = 30) %>%
  hc_yAxis(title = list(text = 'Questionnaire Responses'), labels = list(useHTML = T), max = 30) %>%
  hc_tooltip(pointFormat = '<b>EMR</b>: {point.x:,.0f}</b><br/><b>Questionnaire</b>: {point.y:,.0f}',
               useHTML = T, headerFormat = '') 
# 
# 
# ocs_hc <- highchart() %>%
#   hc_add_series(exac_scatter_test, "scatter", hcaes(response_ehr, response_q), showInLegend = F) %>% 
#   hc_add_series(exac_scatter_test, "line", hcaes(x = response_ehr, y = response_ehr), enableMouseTracking = F, showInLegend = F) %>% 
#   hc_add_dependency("plugins/highcharts-regression.js")%>% 
#   hc_xAxis(title = list(text = 'EMR Responses'), labels = list(useHTML = T), max = 30) %>%
#   hc_yAxis(title = list(text = 'Questionnaire Responses'), labels = list(useHTML = T), max = 30) %>%
#   hc_tooltip(pointFormat = '<b>EMR</b>: {point.x:,.0f}</b><br/><b>Qestionnaire</b>: {point.y:,.0f}',
#                useHTML = T, headerFormat = '') 
# 
# ocs_hc

```

---

# Hosptial Admissions

```{r copd_exac}
ha_exac_0_ehr <- nrow(all_pats1[(all_pats1$hosp_admit == 0),])
ha_exac_1_ehr <- nrow(all_pats1[(all_pats1$hosp_admit == 1),])
ha_exac_2_ehr <- nrow(all_pats1[(all_pats1$hosp_admit == 2),])
ha_exac_3p_ehr <- nrow(all_pats1[(all_pats1$hosp_admit > 2),])

ha_exac_0_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 122 & questionnaire_pats$response == 0),])
ha_exac_1_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 122 & questionnaire_pats$response == 1),])
ha_exac_2_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 122 & questionnaire_pats$response == 2),])
ha_exac_3p_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 122 & questionnaire_pats$response > 2),])

emr_ha <- data.frame(y = round(c(ha_exac_0_ehr, 
                                              ha_exac_1_ehr, 
                                              ha_exac_2_ehr, 
                                              ha_exac_3p_ehr)/total_pats*100,1),
                                    count = format(c(ha_exac_0_ehr, 
                                              ha_exac_1_ehr, 
                                              ha_exac_2_ehr, 
                                              ha_exac_3p_ehr), big.mark = ','))

quest_ha <- data.frame(y = round(c(ha_exac_0_q, 
                                               ha_exac_1_q, 
                                               ha_exac_2_q, 
                                               ha_exac_3p_q)/total_pats*100,1), 
                                     count = format(c(ha_exac_0_q, 
                                               ha_exac_1_q, 
                                               ha_exac_2_q, 
                                               ha_exac_3p_q), 
                                                    big.mark = ','))

exac0_ha <- data.frame(y = c(ha_exac_0_q, ha_exac_0_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac1_ha <- data.frame(y = c(ha_exac_1_q, ha_exac_1_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac2_ha <- data.frame(y = c(ha_exac_2_q, ha_exac_2_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac3p_ha <- data.frame(y = c(ha_exac_3p_q, ha_exac_3p_ehr), 
                      category = c('Questionnaire', 'EMR'))


library(highcharter)
ha_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('Questionnaire', 'EMR')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F)))) %>%
  hc_add_series(name = "3+ Hosptial Admissions", data = exac3p_ha, color = '#E26F2D')%>%
   hc_add_series(name = "2 Hosptial Admissions", data = exac2_ha, color = '#FFA977')%>%
  hc_add_series(name = "1 Hosptial Admission", data = exac1_ha, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Hosptial Admissions", data = exac0_ha, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5) 

ha_exac
```

---

## Hosptial Admission Breakdown

The following outliers were captured in the Questionnaire data and used when calculating the regression line but are not shown on this graph: 

* 1 patient reported 32 Hospital Admissions

```{r ha_exac_scatter, message=FALSE, warning=FALSE}
hosp_admit_q <- filter(questionnaire_pats, question_id == 122)%>% 
  mutate(exac_type = 'Hospital Admission') %>% 
  select(c(opc_patient_id, exac_type, response))%>% 
  rename(patient_id = opc_patient_id, 
         response_q = response)


hosp_admit_ehr <- all_pats1 %>% 
  mutate(exac_type = 'Hospital Admission') %>% 
  select(c(patient_id, exac_type, hosp_admit))%>% 
  rename(response_ehr = hosp_admit)



exac_scatter_ha <- left_join(hosp_admit_ehr, hosp_admit_q, by = c('patient_id', 'exac_type')) %>% 
  distinct(patient_id, exac_type, .keep_all = T)


hchart(exac_scatter_ha, "point", hcaes(response_ehr, response_q), regression = TRUE) %>% 
  hc_colors(c("#d35400", "#2980b9", "#2ecc71")) %>% 
  hc_add_dependency("plugins/highcharts-regression.js") %>% 
  hc_xAxis(title = list(text = 'EMR Responses'), labels = list(useHTML = T), max = 10) %>%
  hc_yAxis(title = list(text = 'Questionnaire Responses'), labels = list(useHTML = T), max = 10) %>%
  hc_tooltip(pointFormat = '<b>EMR</b>: {point.x:,.0f}</b><br/><b>Questionnaire</b>: {point.y:,.0f}',
               useHTML = T, headerFormat = '') 
# 
# ha_hc <- highchart() %>%
#   hc_add_series(exac_scatter_ha, "scatter", hcaes(response_ehr, response_q), showInLegend = F) %>% 
#   hc_add_series(exac_scatter_ha, "line", hcaes(x = response_ehr, y = response_ehr), enableMouseTracking = F, showInLegend = F) %>% 
#   hc_add_dependency("plugins/highcharts-regression.js")%>% 
#   hc_xAxis(title = list(text = 'EMR Responses'), labels = list(useHTML = T), max = 10) %>%
#   hc_yAxis(title = list(text = 'Questionnaire Responses'), labels = list(useHTML = T), max = 10) %>%
#   hc_tooltip(pointFormat = '<b>EMR</b>: {point.x:,.0f}</b><br/><b>Qestionnaire</b>: {point.y:,.0f}',
#                useHTML = T, headerFormat = '') 
# 
# ha_hc
```

---

# General Exacerbations

```{r gen_exac}
gen_exac_0_ehr <- nrow(all_pats1[(all_pats1$exacb_tot_codes == 0),])
gen_exac_1_ehr <- nrow(all_pats1[(all_pats1$exacb_tot_codes == 1),])
gen_exac_2_ehr <- nrow(all_pats1[(all_pats1$exacb_tot_codes == 2),])
gen_exac_3p_ehr <- nrow(all_pats1[(all_pats1$exacb_tot_codes > 2),])

gen_exac_0_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 123 & questionnaire_pats$response == 0),])
gen_exac_1_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 123 & questionnaire_pats$response == 1),])
gen_exac_2_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 123 & questionnaire_pats$response == 2),])
gen_exac_3p_q <- nrow(questionnaire_pats[(questionnaire_pats$question_id == 123 & questionnaire_pats$response > 2),])


emr_gen <- data.frame(y = round(c(gen_exac_0_ehr, 
                                               gen_exac_1_ehr, 
                                               gen_exac_2_ehr, 
                                               gen_exac_3p_ehr)/total_pats*100,1),
                                   count = format(c(gen_exac_0_ehr, 
                                               gen_exac_1_ehr, 
                                               gen_exac_2_ehr, 
                                               gen_exac_3p_ehr), big.mark = ','))

quest_gen <- data.frame(y = round(c(gen_exac_0_q, 
                                                gen_exac_1_q, 
                                                gen_exac_2_q, 
                                                gen_exac_3p_q)/total_pats*100,1), 
                                    count = format(c(gen_exac_0_q, 
                                                gen_exac_1_q, 
                                                gen_exac_2_q, 
                                                gen_exac_3p_q)), 
                                                   big.mark = ',')

exac0_gen <- data.frame(y = c(gen_exac_0_q, gen_exac_0_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac1_gen <- data.frame(y = c(gen_exac_1_q, gen_exac_1_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac2_gen <- data.frame(y = c(gen_exac_2_q, gen_exac_2_ehr), 
                      category = c('Questionnaire', 'EMR'))
exac3p_gen <- data.frame(y = c(gen_exac_3p_q, gen_exac_3p_ehr), 
                      category = c('Questionnaire', 'EMR'))


library(highcharter)
gen_exac <- highchart() %>%
  hc_chart(type = "bar") %>%
  hc_xAxis(type = "category", categories = c('Questionnaire', 'EMR')) %>%
  hc_plotOptions(series = list(stacking = "percent", pointPadding = .1,
                 dataLabels = list(enabled = T, formatter = JS(paste0("function() {
                           if (this.y != 0) {
                            perc = 100 * this.y / this.total
                            return Highcharts.numberFormat(perc,0) + '%';
                           } else {
                            return null;}}")),
                      style = list(textOutline = F))))  %>%
  hc_add_series(name = "3+ Exacerbations", data = exac3p_gen, color = '#E26F2D')%>%
   hc_add_series(name = "2 Exacerbations", data = exac2_gen, color = '#FFA977')%>%
  hc_add_series(name = "1 Exacerbation", data = exac1_gen, color = '#9EB9D4') %>%
  hc_add_series(name = "0 Exacerbations", data = exac0_gen, color = '#0D5295') %>%
    hc_tooltip(pointFormat = '<b>{series.name}</b><br/><b>Count</b>: {point.y:,.0f}<br/><small>Total Patients: {point.total:,.0f}</small>',
               useHTML = T, headerFormat = '') %>%
    hc_legend(reversed = T) %>%
    hc_yAxis(labels = list(format = "{value}%"), tickInterval = 10, minorTicks = T, minorTickInterval = 5) 

gen_exac
```

---

## General Exacerbation Breakdown

The following outliers were captured in the Questionnaire data and used when calculating the regression line but are not shown on this graph: 

* 1 patient reported 2,222 General Exacerbations


```{r gen_exac_scatter, message=FALSE, warning=FALSE}
gen_q <- filter(questionnaire_pats, question_id == 123)%>% 
  mutate(exac_type = 'General exacerbation') %>% 
  select(c(opc_patient_id, exac_type, response)) %>% 
  rename(patient_id = opc_patient_id, 
         response_q = response)

gen_ehr <- all_pats1 %>% 
  mutate(exac_type = 'General exacerbation') %>% 
  select(c(patient_id, exac_type, exacb_tot_codes)) %>% 
  rename(response_ehr = exacb_tot_codes)


exac_scatter_gen <- left_join(gen_ehr, gen_q, by = c('patient_id', 'exac_type')) %>% 
  distinct(patient_id, exac_type, .keep_all = T)

hchart(exac_scatter_gen, "point", hcaes(response_ehr, response_q), regression = TRUE) %>% 
  hc_colors(c("#d35400", "#2980b9", "#2ecc71")) %>% 
  hc_add_dependency("plugins/highcharts-regression.js") %>% 
  hc_xAxis(title = list(text = 'EMR Responses'), labels = list(useHTML = T), max = 10) %>%
  hc_yAxis(title = list(text = 'Questionnaire Responses'), labels = list(useHTML = T), max = 10) %>%
  hc_tooltip(pointFormat = '<b>EMR</b>: {point.x:,.0f}</b><br/><b>Questionnaire</b>: {point.y:,.0f}',
               useHTML = T, headerFormat = '') 

# 
# gen_hc <- highchart() %>%
#   hc_add_series(exac_scatter_gen, "scatter", hcaes(response_ehr, response_q), showInLegend = F) %>% 
#   hc_add_series(exac_scatter_gen, "line", hcaes(x = response_ehr, y = response_ehr), enableMouseTracking = F, showInLegend = F) %>% 
#   hc_add_dependency("plugins/highcharts-regression.js")%>% 
#   hc_xAxis(title = list(text = 'EMR Responses'), labels = list(useHTML = T), max = 10) %>%
#   hc_yAxis(title = list(text = 'Questionnaire Responses'), labels = list(useHTML = T), max = 10) %>%
#   hc_tooltip(pointFormat = '<b>EMR</b>: {point.x:,.0f}</b><br/><b>Qestionnaire</b>: {point.y:,.0f}',
#                useHTML = T, headerFormat = '') 
# 
# gen_hc
```

---